### 2011-09-25 doc/theses/vitasek/chapter-3-mip.tex
Thesis: in progress.

TODO rigorously define MIP - optimization problem similar to LP, however some of the variables integral or boolean

TODO FIDAX is cool, but their heuristic might not be the best. It is a IS problem, let's try a multi-purpose solver. Use GLPK. \nomenclature{GLPK}{GNU Linear Programming Kit}

@@

We can use this as an input for the GLPK solver, and we get the solution: TODO GLPK output.

 -> wow, GLPK works. However, it takes too long to get to optimum (link experiments), so let's try other heuristics.

>>>>

We have shown that ID set -> IS, now we show the translation to MIP formulation and solve it using GLPK. \nomenclature{GLPK}{GNU Linear Programming Kit}

TODO MIP formulation: LP is simple using Simplex method, however as soon as we require integrality or boolean values, it is NP-hard.

\begin{define}[Mixed integer problem]
	MIP, or \textit{mixed integer problem}, is an instance of linear programming in which some variables are limited to integral or boolean (0, 1) values.
\end{define}

TODO show how to translate IS to MIP

@@

We can use this as an input for the GLPK solver, and we get the solution.

\begin{scriptsize}
\begin{verbatim}
...
Problem:    glpk_input
Rows:       5
Columns:    4 (4 integer, 4 binary)
Non-zeros:  12
Status:     INTEGER OPTIMAL
Objective:  z = 0.6 (MAXimum)

...

   No. Column name       Activity     Lower bound   Upper bound
------ ------------    ------------- ------------- -------------
     1 x[y-a]       *              1             0             1 
     2 x[y-b]       *              0             0             1 
     3 x[y-c]       *              0             0             1 
     4 x[z-a]       *              0             0             1

...
\end{verbatim}
\end{scriptsize}

This output tells us that the solution is $x_{y-a} = 1$, $x_{y-b} = 0$, $x_{y-c} = 0$ and $x_{z-a} = 0$. This means that the optimal ID set with maximum weight contains only the $M_{y}^{a}$ attribute mapping.\\

It is obvious that this approach works and for any possible input we can let GLPK find the optimal solution. However, sometimes it takes too long to find the optimum (see e.g. Section \ref{section-glpk-comparison}), we should try to improve this process.

### 2011-09-25 doc/theses/vitasek/chapter-6-conclusion.tex
Thesis: in progress.

TODO conclusion: From all integrity constraints in XML we chose the ID attributes and decided to improve the search for them. We discussed the approach chosen in FIDAX. Based on this article we introduced the MIP approach and demonstrated how to find the optimal (w.r.t. weight) ID set.

However, this approach takes too long for some inputs, so we introduced a whole spectrum of construction as well as improvement heuristics. By combining these algorithms and tuning their parameters we were able to find very good solutions while maintaining low running times.

>>>>

From all the integrity constraints in XML we chose the ID / IDREF / IDREFS attributes and decided to improve upon the search for them. We discussed the approach from \cite{fidax} and the equivalence of ID set search and maximum weighted independent set. Based on this article we introduced the MIP approach and demonstrated how to find the optimal ID set using external GLPK solver in the environment of jInfer framework.\\

However, this approach took too long for some inputs, so we introduced a whole range of construction as well as improvement heuristics. We combined these algorithms to create a metaheuristic and performed a number of experiments to understand its behavior. Finally we selected a promising metaheuristic strategy and tuned its parameters to find very good ID sets while maintaining low running times.\\

To the best of our knowledge, at the time of writing this work is our approach to finding ID attributes the best one known.
